|

### 2024-08-02 lectures/week1/week1a.Rmd
update slides

\vfill
- Course overview
\vfill
- Detailed outline
\vfill
- Grade breakdown
\vfill
- Course website on github: https://github.com/rmadhok/enviro-dev-grad
  - lecture slides, assignments, syllabus

@@

For students specializing in environment/development:

1. Show you research frontier

@@

For other students:

@@

## Broad Breakdown

@@

- At start of each lecture (from week 2), you will present a paper for 15 minutes

- Each student reads paper and submits **seven** slides (5% of grade)
  - motivation, research question, methods, results
  - 10 mins presentation + 5 mins Q&A (5% of grade)

- I will select presenter **randomly** with replacement**

>>>>

\vfill
- Course overview
\vfill
- Detailed outline
\vfill
- Grade breakdown
\vfill
- Course website: https://github.com/rmadhok/enviro-dev-grad
  - lectures, assignments, syllabus

@@

1. Show you environment/development research frontier

@@

@@

## Breakdown

@@

- At start of **first** lecture each week, you'll give a 15 min paper presentation

- Each student submits **seven** summary slides (5% of grade)
  - motivation, research question, methods, results
  - 10 mins presentation + 5 mins Q&A (5% of grade)

- I will select presenter on-the-spot 
  - **randomly** with replacement**
